resistanceModelNotesAndy

### 2015-07-08 resistanceModelNotesAndy.Rmd
notes

@@

1. should I create a little shiny app mimicing curtis fig2, & allowing usr to modify params, to see how to keep the mixtures doing better ?

>>>>

created runcurtis_f2() to do runs to recreate curtis fig2. recreates it fine.

created shinyFig2Curtis, that calls runcurtis_f2()

for some reason it currently doesn't recreate the curtis plot.
what inputs are wrong in shinyFig2Curtis ?
aha! the difference was just `P_1 & P_2` which were set to 0.1 rather than 0.01
aha2, even after that fixed, something still not quite right

this was because phi.SS2_0B = 1 was set to 0 instead. This is the fitness of exposed susceptibles.
(1 suggests that the susceptible is completely fit in presence of the insecticide which doesn't seem right).

yes phi.SS2_0B seems key :
compare these 2:
```{r}
#curtis default phi.SS2_0B = 1 : mixture better than sequence
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
#reduce phi.SS2_0B to 0.6 : mixture same as sequence
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.6 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )

How does that relate to this comment from the paper ?
In particular, Curtis [1] allowed the resistant and sensitive homozygotes to survive DDT exposure with finesses of 50% and 27% respectively (caption to his Figure 2).

@@

1. why can't shinyapps find resistance for this :
Deployment completed: https://andysouth.shinyapps.io/shinyFig2Curtis
Warning message:
In FUN(X[[i]], ...) :
  Package 'resistance' not available in repository or locally

1. work out what to do if critical threshold not reached in findResistancePoints()
causes : Error in plot.window(...) : need finite 'xlim' values
